\documentclass[a4paper,12pt]{book}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\usepackage{lipsum}
%\usepackage[utf8]{inputenc}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{tcolorbox}
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\usepackage{mathtools}
%\hypersetup{
%	colorlinks=true, %set true if you want colored links
%	linktoc=all,     %set to all if you want both sections and subsections linked
%	linkcolor=blue,  %choose some color if you want links to stand out
%	linktocpage
%}
\begin{document}

\author{Pugazharasu}
\title{Mathematical Physics}
\date{July 2020}

\frontmatter
\maketitle
\pagebreak
\chapter*{Preface}
This document is simply the collective summary of all of the fundamental mathematics that I have learnt over the years. This assumes a little mathematical maturity. More niche subjects such as analysis, topology and Lie theory are relegated in separate documents. This should only be treated as a revision/recall document and not as a learning material since it is devoid of lenghty explanations and often assumes you have at least briefly read through the cited texts or similar material.
\nopagebreak
\tableofcontents


%\pagebreak

\addcontentsline{toc}{chapter}{Preface}

\mainmatter
%\include{./TeX_files/chapter-2}
%\include{./TeX_files/chapter-1}
%\include{./TeX_files/chapter00}
%\include{./TeX_files/chapter01}
%\include{./TeX_files/chapter02}
%\include{./TeX_files/chapter03}
\include{./TeX_files/chapter04}
\include{./TeX_files/chapter05}
\include{./TeX_files/chapter06}
\include{./TeX_files/chapter07}
\include{./TeX_files/chapter08}
\include{./TeX_files/chapter09}
\include{./TeX_files/chapter10}
\include{./TeX_files/chapter11}
\include{./TeX_files/chapter12}
\backmatter
\begin{thebibliography}{9}
	\bibitem{arxivmath}
	Jean Claude Dutailly.
	\textit{Mathematics for theoretical physics}.
	arXiv:1209.5665v2
	
	\bibitem{latexcompanion} 
	Michel Goossens, Frank Mittelbach, and Alexander Samarin. 
	\textit{The \LaTeX\ Companion}. 
	Addison-Wesley, Reading, Massachusetts, 1993.
	
	\bibitem{Nathan} 
	Nathan Carter 
	\textit{Visual Group Theory}. 
	Annalen der Physik, 322(10):891–921, 1905.
	
	\bibitem{Munkres} 
	James R. Munkres 
	\textit{Topology}.
	Annalen der Physik, 322(10):891–921, 1905.
	
	\bibitem{Stillwell} 
	John Stillwell 
	\textit{Naive Lie Theory}. 
	Annalen der Physik, 322(10):891–921, 1905.
	
	\bibitem{Artin} 
	Michael Artin 
	\textit{Algebra}Computers and Typesetting,
	\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}
\end{thebibliography}
% bibliography, glossary and index would go here.

\end{document}